\newgeometry{
left=4cm,
right=2.5cm,
top=2cm,
bottom=4cm}
\chapter*{Acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}

After spending almost a third of my life in Glasgow, pursuing both my undergraduate and postgraduate studies at Strathclyde, I am deeply grateful to everyone who has made this journey unforgettable and supported me every step of the way. \\

First and foremost, I would like to express my heartfelt thanks to my supervisor, Andrew Daley, for granting me the opportunity to undertake this PhD under his exceptional guidance and unwavering support. Under his mentorship, I have acquired a wealth of knowledge in physics and honed numerous skills that have prepared me for my professional career. \\

I am also profoundly grateful to my fellow PhD students and post-docs in our group: Callum, François, Gerard, Johannes, Liam, Rosaria, and Sridevi. Special thanks go to Jorge for being a true friend and providing immense help throughout my PhD. I would also like to acknowledge Jacopo, Stuart, and Tomohiro, who were always ready to offer their assistance whenever needed. \\

Next, I extend my gratitude to my friends: Ahmed, Amine, and Athina, for their companionship since our first days in Glasgow; Eduardo, for sharing countless dark beverages and making music together; Iro, for her friendship and for showing me the beauty of Athens; the Shuttlecock Destroyers—Jack, Johan, and Jorge—for the fun and camaraderie on the badminton court; and finally Nicole, for being an incredible flatmate and the greatest prankster I've had the pleasure to meet. \\

I am especially thankful to my girlfriend, Maria, for her unwavering support, particularly during the challenging process of writing this thesis. Her motivation and encouragement have been invaluable. \\

Finally, I would like to thank my family for their support throughout this journey. Their encouragement has always driven me to strive for better. Merci.

\vspace{1cm}
\hspace*{\fill} \textit{Bintener Tom, 01.09.2023}

\cleardoublepage
\restoregeometry