\newgeometry{
left=4cm,
right=2.5cm,
top=2cm,
bottom=4cm
}

\chapter*{Preface}
\addcontentsline{toc}{section}{Preface}

In May 2019, I started working on the project that is the focus of chapter~\ref{chap:MIPT_bosons}. Towards the final stages of the project in 2020, we became aware of a paper \cite{fuji2020}, which investigated a very similar model, which led to the decision not to publish our manuscript. Regardless of this decision, I have contributed to new insight into the physics of measurement-induced phase transitions in continuous-time systems. I explored and analyzed different models and presented transitions manifesting in the entanglement entropy in individual trajectories, presented in chapter~\ref{chap:MIPT_bosons}.

Moreover, I have expanded our understanding of why these transitions are so difficult to measure directly in experiments. Although some quantities, like the entanglement entropy, visualize the transition quite clearly, the exact location of the transition is quite difficult to pinpoint. This difficulty is also discussed in chapter~\ref{chap:MIPT_bosons}, and the presented analysis provides new insight into the difficulties that were not discussed in the existing literature. Furthermore, I proved why, in a homodyne detection scheme, you cannot use the measurement outcomes to reconstruct nonlinear functions that witness the transition. The reason why this is the case is subtle, and it is the focus of chapter~\ref{chap:MIPT_continuous_measurement}.

Lastly, I have explored the consequences of competition between dissipative and coherent processes for many-body dynamics at short to medium times. I have investigated the signatures of the transitions we can observe at short times in models that undergo phase transitions in the long time limit of non-linear functions of the density operator. In addition, I have explored how this short-time competition might be investigated. This topic is the focus of chapter~\ref{chap:short_time_dynamics}. \\

Overall, I have generated both new theoretical understanding, of interest to theorists in this particularly topical area, and also experimental proposes, especially for exploring competition between coherent and dissipative processes in short-time dynamics. \\

\textbf{Publications during the Ph.D.}
\begin{enumerate}
    \item \fullcite{bintener2024}

    This paper is the topic of chapter~\ref{chap:short_time_dynamics}. To be submitted to Physical Review A, 2024.
\end{enumerate}

\cleardoublepage